### 2022-03-30 satfol/satfol.tex

The most important novel aspect of our predicate elimination implementation is
recognizing the definition clauses for symbol $\cst{p}$ in a clause set $N$, which is performed
as follows, assuming $\tupleempty{x}$ is a fixed tuple of distinct free variables:
\begin{enumerate}
   \item Let $G = \{ C \mid C = \arbpredlit{\cst{p}(\tupleempty{y})} \cor C', C \in
   N$, no variable repeats in $\tupleempty{y}$, and the variables of $C'$ are among
   $\tupleempty{y}\}$. If $G$ is empty, report failure; otherwise, continue.

@@

%    \smallskip
   \item\label{step:encoding} Let $\lfloor a \rfloor$ be a function that assigns
   a propositional variable to each atom $a$. This function is lifted to
   literals by assigning $\lfloor \neg a \rfloor  = \neg x$ if $\lfloor a
   \rfloor = x$, and to clauses pointwise. Furthermore,  
   let $E = \{ \lfloor C' \rfloor \mid
   \arbpredlit{\cst{p}(\tupleempty{x})} \cor C' \in G \}$. If $E$ is satisfiable,
   report failure. Else, let $E'$ be the unsatisfiable core of $E$
   and $G'$ the set of corresponding first-order clauses and continue.

%    \smallskip
   \item If all resolvents in $G'_{\pospredlit{\cst{p}}} \flatres_{\!\cst{p}}
   G'_{\negpredlit{\cst{p}}}$ are tautologies, then $G'$ is the definition set
   for symbol $\cst{p}$. Else, report failure.
\end{enumerate}

>>>>

The most important novel aspect of our predicate elimination implementation is
recognizing the definition clauses for a symbol $\cst{p}$ in a clause set $N$, which is performed
as follows, assuming $\tupleempty{x}$ is a fixed tuple of distinct free variables:
\begin{enumerate}
   \item Let $G = \{ C \mid C = \arbpredlit{\cst{p}(\tupleempty{y})} \cor C', C \in
   N$, no variable repeats in $\tupleempty{y}$, and the variables of $C'$ are all among
   $\tupleempty{y}\}$. If $G$ is empty, report failure; otherwise, continue.

@@

%    \smallskip
   \item\label{step:encoding} Let $\lfloor a \rfloor$ be a function that assigns
   a propositional variable to each atom $a$. This function is lifted to
   literals by assigning $\lfloor \neg a \rfloor  = \neg x$ if $\lfloor a
   \rfloor = x$, and to clauses pointwise. Furthermore,  
   let $E = \{ \lfloor C' \rfloor \mid
   \arbpredlit{\cst{p}(\tupleempty{x})} \cor C' \in G \}$. If $E$ is satisfiable,
   report failure. Otherwise, let $E'$ be an unsatisfiable core of $E$
   and $G'$ the set of corresponding first-order clauses and continue.

%    \smallskip
   \item If all resolvents in $G'_{\pospredlit{\cst{p}}} \flatres_{\!\cst{p}}
   G'_{\negpredlit{\cst{p}}}$ are tautologies, then $G'$ is a definition set
   for symbol $\cst{p}$. Otherwise, report failure.
\end{enumerate}

### 2022-03-30 summary/summary.tex
concl

\looseness=-1
In the last decades, proof assistants were immeasurably useful in formally
proving validity of hard mathematical theories and correctness of
safety-critical software. These tools provide a formal language that allows one
to describe a problem and prove statements about it which are later
automatically checked. To make the checking phase efficient and trustworthy,
proof steps need to be of high granularity. As a consequence, seemingly
simple statements must be proven in minute detail, making the use of proof
assistants very tedious.

@@

After testing out our ideas in Zipperposition, we decided to go back to Ehoh and
extend it to full higher-order logic, obtaining a prover called \ehohii{}. We
choose the most successful approaches implemented in Zipperposition that can
easily be ported to \ehohii{}. The results were once again positive: Our
evaluation shows that \ehohii{} is the best prover on proof assistant
benchmarks, and second only to Zipperposition on a standard benchmark set.

@@

  Samenvatting in het Nederlands.
}

>>>>

\looseness=-1
In the last decades, proof assistants were immeasurably useful in formally
proving validity of hard mathematical theories and correctness of
safety-critical software. Using these tools one can formally describe a problem
and produce machine-checkable proofs for statements about it. To make the
checking phase efficient and trustworthy, proof steps need to be of high
granularity. As a consequence, seemingly simple statements must be proven in
minute detail, making the use of proof assistants very tedious.

@@

After testing out our ideas in Zipperposition, we decided to go back to Ehoh and
extend it to full higher-order logic, obtaining a prover called \ehohii{}. We
chose the most successful approaches implemented in Zipperposition that can
easily be ported to \ehohii{}. The results were once again positive: Our
evaluation shows that \ehohii{} is the best prover on proof assistant
benchmarks, and second only to Zipperposition on a standard benchmark set.

@@

}

### 2022-03-30 title/title.tex
more

%% List the promotors (supervisors).
\medskip\noindent
\begin{tabular}{ll}
    promotor: & prof.dr. W. J. Fokkink \\
    copromotoren: & dr. J. C. Blanchette \\
                  & prof.$\,$dr. S. Schulz
\end{tabular}

@@

prof.$\,$dr. Mark Hoogendoorn & Vrije Universiteit Amsterdam \\
dr. Konstantin Korovin & The University of Manchester \\
dr. Ruzica Piskac & Yale University \\
dr. Alexander Steen & University of Greifswald \\
dr. Martin Suda & Czech Technical University in Prague \\
prof.$\,$dr. Geoff Sutcliffe & University of Miami \\

>>>>

%% List the promotors (supervisors).
\medskip\noindent
\begin{tabular}{ll}
    promotor: & prof.$\,$dr. W. J. Fokkink \\
    copromotoren: & dr. J. C. Blanchette \\
                  & prof.$\,$dr. S. Schulz
\end{tabular}

@@

prof.$\,$dr. M. Hoogendoorn & Vrije Universiteit Amsterdam \\
dr. K. Korovin & The University of Manchester \\
dr. R. Piskac & Yale University \\
dr. A. Steen & University of Greifswald \\
dr. M. Suda & Czech Technical University in Prague \\
prof.$\,$dr. G. Sutcliffe & University of Miami \\
